First Order Alternation

### 2018-09-14 quantifiers/draft.tex
ok

Given formulae $\phi$ and $\psi$ such that $\phi \wedge \psi$ is
unsatisfiable, a \emph{Lyndon interpolant} \cite{Lyndon59} is a
first-order formula $I$ such that: \begin{compactitem}
\item the formula $\phi \rightarrow I$ is valid,
\item the formula $I \wedge \psi$ is unsatisfiable, 
\item $\voc{I} \subseteq \voc{\phi} \cap \voc{\psi}$, 
\item $\pset{+}{I} \subseteq \pset{+}{\phi} \cap \pset{+}{\psi}$ and
  $\pset{-}{I} \subseteq \pset{-}{\phi} \cap \pset{-}{\psi}$.
\end{compactitem}
The existence of Lyndon interpolants for first-order logic was proved
by a non-constructive model-theoretic argument \cite{Lyndon59}. In the
following, we shall consider only theories of the data domain $\Data$,
for which there exists a decision procedure for satisfiability, able
to produce Lyndon interpolants. For instance, interpolating decision
procedures exist for linear real and integer arithmetic, with
uninterpreted function symbols (UFLRA and UFLIA)
\cite{RybalchenkoSofronieStokkermans}. In the rest of this section, we
fix an automaton $\A = \tuple{\Sigma,X,Q,\iota,F,\Delta}$.

>>>>

\begin{definition}\label{def:lyndon-interpolant}
Given formulae $\phi$ and $\psi$ such that $\phi \wedge \psi$ is
unsatisfiable, a \emph{Lyndon interpolant} \cite{Lyndon59} is a
formula $I$ such that $\phi \models I$, the formula $I \wedge \psi$ is
unsatisfiable, $\voc{I} \subseteq \voc{\phi} \cap \voc{\psi}$,
$\pset{+}{I} \subseteq \pset{+}{\phi} \cap \pset{+}{\psi}$ and
$\pset{-}{I} \subseteq \pset{-}{\phi} \cap \pset{-}{\psi}$.
\end{definition}
The existence of Lyndon interpolants for first-order logic was proved
by a non-constructive model-theoretic argument \cite{Lyndon59}. In the
following, we shall consider only theories of the data domain $\Data$,
for which there exists a decision procedure for satisfiability, able
to produce Lyndon interpolants. For instance, such interpolating
decision procedures exist for linear real and integer arithmetic, with
uninterpreted function symbols (UFLRA and UFLIA)
\cite{RybalchenkoSofronieStokkermans}. In the rest of this section, we
fix an automaton $\A = \tuple{\Sigma,X,Q,\iota,F,\Delta}$.
